\LaTeXe\ guide for the Journal of Functional Programming

### 2019-11-08 papers/jfp/1-intro.tex
Minor tweaks

\item Moreover, we can readily remix the ingredients to design new build systems
with desired properties, for example, to combine the advantages of \Shake and
\Bazel. Writing this paper gave us the insights to combine dynamic dependencies and
cloud build in a principled way; we evaluate the result~(\S\ref{sec-experience}).

>>>>

\item Moreover, we can readily remix the ingredients to design new build systems
with desired properties, for example, to combine the advantages of \Shake and
\Bazel. Writing this paper gave us the insights to combine dynamic dependencies
and cloud build systems in a principled way; we evaluate the result
in~\S\ref{sec-experience}.

### 2019-11-08 papers/jfp/2-background.tex
Wibbles
Minor tweaks

\noindent
This property is tightly linked to build system \emph{correctness}, which we
will be ready to define in~\S\ref{sec-build-correctness}; for now, we will use
minimality as the guiding principle when exploring the design space of build
systems.

@@

\subsection{\Shake: Dynamic Dependencies with No Remorse}
\label{sec-background-shake}

>>>>

\noindent
This property is tightly linked to build system \emph{correctness}, which we
will be ready to define in~\S\ref{sec-build-correctness}; for now, we will use
minimality as a guiding principle when exploring the design space of build
systems.

@@

\subsection{\Shake: Dynamic Dependencies without Remorse}
\label{sec-background-shake}
